The Jester joke recommender system

### 2020-08-24 inst/jester.Rmd
names paradigm changes

```{r,label=calculate_jester,cache=TRUE}
jester <- hyper2(pnames=colnames(a))
system.time(for(i in seq_len(nrow(a))){jester %<>% order_obs(f(a[i,]))})
```

>>>>

```{r,label=calculate_jester,cache=TRUE}
jester <- hyper2()
system.time(for(i in seq_len(nrow(a))){jester <- jester + rank_likelihood(f(a[i,]))})
```
